---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE, }
knitr::opts_chunk$set(collapse=TRUE, comment="##", fig.retina=2, fig.path = "README_figs/README-")
library(tidyverse)
```

## `panelAppR`: An R package to intefrace with the PanelApp API

### Installation
```{r, eval=FALSE}
devtools::install_github("bahlolab/panelappR")
```

### Usage

* Both [PanelApp Australia](https://panelapp.agha.umccr.org/) and [Genomics England PanelApp](https://panelapp.genomicsengland.co.uk/) are available. To access PanelApp Australia use `db = 'AGHA'`, and for Genomics England use `db = 'GE'`.
* The function `list_panels` lists all available panels from a given source.
* The function `get_panel` retrieves a specific panel by id.

```{r example_1}
panelappR::list_panels(db = 'AGHA') %>% 
  head()
```

```{r example_2}
panelappR::get_panel(id = 3149, db = 'AGHA') %>% 
  head()
```

```{r example_3}
panelappR::list_panels(db = 'GE') %>% 
  head()
```
```{r example_4}
panelappR::get_panel(id = 933, db = 'GE') %>% 
  head()
```
### Not (Yet) Implemented

* Error checking (i.e. attempt to retrieve a non-existant panel)
* Version specific queries - currently only the latest version of a panel is returned
